Which ITG Stepcharts are Turniest?

### 2017-03-15 itg/2/paper.tex
update tables

% Stuff to talk about.
% Dataset size now >10k
% I reran turniness on fancy footwork and it actually got turnier (double check dis), b/c of all the candles

@@

\begin{figure}[t]

@@

	\begin{tabular}{r|l|l|c}

@@

		\multicolumn{4}{c}{\em no 8s- with $\ge$100 XOs} \\

@@

		15 & MAX Forever              & CuoReNeRo & 101 \\
		\multicolumn{4}{c}{\em no 16s-20s with $\ge$100 XOs} \\

@@

		%\bf Ft. & \bf Name & \bf Pack & \bf \#XO & \bf XO\% \\
		%\hline
		%\multicolumn{5}{c}{\em no 8s- with $\ge$100 XOs} \\
		% 9 & MAX Forever              & CuoReNeRo MeGaPacK    & \bf 107 & \em 8.7 \\
		%10 & J-PARA SUPER MEGAMIX     & CuoReNeRo MeGaPacK    & \bf 141 & \em 3.9 \\
		%11 & Somebody That I Used To Know & Best of Gazebo    & \bf 114 & \em 11.9 \\
		%12 & Credens Justitiam        & Stuff B Likes         & \bf 136 & \em 12.4 \\
		%13 & Banshee Strikes          & VocaJawnz             & \bf 152 & \em 10.2 \\
		%14 & Slow Down                & Sexuality Violation 2 & \bf 160 & \bf 13.3 \\
		%15 & MAX Forever              & CuoReNeRo MeGaPacK    & \bf 101 & \em 4.2 \\
		%\multicolumn{5}{c}{\em no 16s-20s with $\ge$100 XOs} \\
		%21 & Teenage Dream            & Sexuality Violation 2 & \bf 280 & \bf 11.8 \\

@@

\end{figure}
\begin{figure}[t]

@@

		\multicolumn{4}{c}{\em no 15s-20s with $\ge$10\% XOs} \\

@@

		%\bf Ft. & \bf Name & \bf Pack & \bf \#XO & \bf XO\% \\
		%\hline
		% 4 & DAM DIRIRAM              & DDR 3rdMIX            & \em  30 & \bf 27.3 \\
		% 5 & STRICTLY BUSINESS        & DDR 1st               & \em  33 & \bf 21.4 \\
		% 6 & STRICTLY BUSINESS        & DDR 1st               & \em  38 & \bf 20.9 \\
		% 7 & MOBO$\star$MOGA          & DDR EXTREME           & \em  37 & \bf 17.3 \\
		% 8 & PARANOiA                 & DDR 1st               & \em  58 & \bf 19.6 \\
		% 9 & Dazzlin Darlin           & r21twins              & \em  76 & \bf 22.0 \\
		%10 & Enchanted Journey        & ITG Rebirth           & \em  78 & \bf 19.3 \\
		%11 & Lune Noir                & r21freak Friendship   & \em  58 & \bf 13.4 \\
		%12 & Winnipeg is Fucking Over & best of r21freak ii   & \em 122 & \bf 14.3 \\
		%13 & The Sampling Paradise    & The Paradise Sampler  & \em 139 & \bf 15.6 \\
		%14 & Slow Down                & Sexuality Violation 2 & \bf 160 & \bf 13.3 \\
		%\multicolumn{5}{c}{\em no 15s-20s with $\ge$10\% XOs} \\
		%21 & Teenage Dream            & Sexuality Violation 2 & \bf 280 & \bf 11.8 \\

@@

		\multicolumn{4}{c}{\em no 5s- with $\ge$50 FSs} \\

@@

		\multicolumn{4}{c}{\em no 7s-9s with $\ge$50 FSs} \\

@@

		\multicolumn{4}{c}{\em no 17s+ with $\ge$50 FSs} \\
		%\bf Ft. & \bf Name & \bf Pack & \bf \#FS & \bf FS\% \\
		%\hline
		%\multicolumn{5}{c}{\em no 5s- with $\ge$50 FSs} \\
		% 6 & Sweat Shop       & ITG Rebirth 2 Beta    & \bf  56 & \bf 18.2 \\
		%\multicolumn{5}{c}{\em no 7s-9s with $\ge$50 FSs} \\
		%10 & Eat 'Em Up!      & Mute Sims 5           & \bf  54 & \em  9.0 \\
		%11 & Nemeton          & The Legend of Zim 4   & \bf  97 & \em 10.3 \\
		%12 & Nemeton          & Subluminal            & \bf 140 & \bf 14.8 \\
		%13 & Love Is Eternity & Subluminal            & \bf 140 & \bf 16.8 \\
		%14 & Switch           & Getty                 & \bf 347 & \bf 15.7 \\
		%15 & Danse Macabre    & Aoreo's Ariginals     & \bf 201 & \em 12.2 \\
		%16 & Weird Science    & Stamina Showcase      & \bf  61 & \em  1.8 \\
		%\multicolumn{5}{c}{\em no 17s+ with $\ge$50 FSs} \\

@@

		 4 & MAKE IT BETTER   & DDR 2ndMIX            & 20.0 \\
		\multicolumn{4}{c}{\em no 5s with $\ge$10\% FS} \\

@@

		\multicolumn{4}{c}{\em no 8s with $\ge$10\% FS} \\

@@

		\multicolumn{4}{c}{\em no 16s+ with $\ge$10\% FS} \\
		%\bf Ft. & \bf Name & \bf Pack & \bf \#FS & \bf FS\% \\
		%\hline
		% 3 & Sweat Shop       & ITG Rebirth 2 Beta    & \em  26 & \bf 15.3 \\
		% 4 & MAKE IT BETTER   & DDR 2ndMIX            & \em  26 & \bf 20.0 \\
		%\multicolumn{5}{c}{\em no 5s with $\ge$10\% FS} \\
		% 6 & Sweat Shop       & ITG Rebirth 2 Beta    & \bf  56 & \bf 18.2 \\
		% 7 & 5.1.1            & DDR MAX               & \em  13 & \bf 12.9 \\
		%\multicolumn{5}{c}{\em no 8s with $\ge$10\% FS} \\
		% 9 & PARANOiA KCET    & DDR 2ndMIX            & \em  33 & \bf 10.2 \\
		%10 & Delhi Ill        & Mute Sims 6           & \em  40 & \bf 11.6 \\
		%11 & Sweat Shop       & ITG Rebirth 2 Beta    & \em  75 & \bf 11.8 \\
		%12 & Nemeton          & Subluminal            & \bf 140 & \bf 14.8 \\
		%13 & Love Is Eternity & Subluminal            & \bf 140 & \bf 16.8 \\
		%14 & Switch           & Getty                 & \bf 347 & \bf 15.7 \\
		%15 & Flames of the Sky & fort rapids vii      & \em 172 & \bf 16.5 \\
		%\multicolumn{5}{c}{\em no 16s+ with $\ge$10\% FS} \\

@@

		12 & Beautiful Synergy & Keyboard Collaboration III & 14 \\

@@

		% 9 & Dr. Boom-Bombay   & fort rapids vii            & \bf 18 & 4.0 \\
		%10 & Toxic             & Sexuality Violation 2      & \bf 12 & 1.5 \\
		%11 & Heart Shooter     & VocaJawnz                  & \bf 44 & 5.1 \\
		%12 & Beautiful Synergy & Keyboard Collaboration III & \bf 14 & 3.2 \\
		%13 & Toxic             & Sexuality Violation 2      & \bf 12 & 1.2 \\
		%14 & Fancy Footwork    & Cirque du Zeppelin         & \bf 40 & 4.2 \\

@@

\end{figure}

>>>>

% Stuff to talk about.
% Dataset size now >10k
% I reran turniness on fancy footwork and it actually got turnier (double check dis), b/c of all the candles
% 9-15 is clearly the sweet spot for techni jawnz

@@

% charts
\begin{table}[t]

@@

	\begin{tabular}{r|l|l|l}

@@

		 6 & Autoload                 & ITG 3                 &  54 \\
		 7 & Tetris                   & CuoReNeRo             &  58 \\
		 8 & Pulse                    & CuoReNeRo             &  94 \\

@@

		15 & yoshikawa45 vs siesta45  & Rikame's Simfiles 4   & 111 \\
		16 & Your Best Nightmare      & Undertale             &  97 \\
		\multicolumn{4}{c}{\em no 17s-19s with $\ge$50 XOs} \\
		20 & Rainbow Dimension        & Rikame's Simfiles 2   &  84 \\

@@

@@

\end{table}
\begin{table}[t]

@@

		15 & yoshikawa45 vs siesta45  & Rikame's Simfiles 4   & 10.8 \\
		\multicolumn{4}{c}{\em no 16s-19s with $\ge$10\% XOs} \\
		20 & Rainbow Dimension        & Rikame's Simfiles 2   & 10.7 \\

@@

@@

		%\multicolumn{4}{c}{\em no 5s- with $\ge$50 FSs} \\

@@

		 7 & Silent Hill      & DDR 3rdMIX            &  29 \\
		 8 & Pulse            & CuoReNeRo             &  41 \\
		 9 & Dr. Boom-Bombay  & fort rapids vii       &  34 \\

@@

		17 & Arcane Apparatus & Tachyon Gamma         &  32 \\
		18 & Metallic-A-      & Oh Henry! Mad Stamina &  27 \\
		19 & Geronimo         & Sexuality Violation 3 &  39 \\
		20 & Scatman's World  & Jimmy Jawns 2         &  22 \\
		21 & He He He         & Jimmy Jawns 2         &   4 \\
		22 & Architecture     & SPEEEDCOOOORE 4       &  24 \\
		23 & Geronimo         & Sexuality Violation 3 &  39 \\

@@

		 4 & DROP THE BOMB    & DDR 3rdMIX            &  9.8 \\
		 5 & MAKE IT BETTER   & DDR 2ndMIX            & 20.0 \\

@@

		 8 & La Se\~{n}orita Virtual & DDR 3rdMIX     &  8.4 \\

@@

		16 & Mermaid Island   & Tachyon Alpha         &  9.5 \\
		\multicolumn{4}{c}{\em no 17s+ with $\ge$5\% FS} \\

@@

		12 & Beautiful Synergy & Keyboard Collab. III & 14 \\

@@

		15 & yoshikawa45 vs siesta45 & Rikame's Simfiles 4  & 20 \\

@@

\end{table}

% authors
\begin{table}[t]
	\begin{center}
		\small
	\begin{tabular}{l|r|r|l}
		\bf Author & \bf Charts & \bf Total Steps & \bf FS\% \\
		\hline
		Konami        & 530 & 114623 & 8.03 \\
		sssmsm        &  41 &  17219 & 6.55 \\
		NEMORIGINAL   &  44 &  20165 & 5.36 \\
		M. Emirzian   &  23 &   9307 & 5.16 \\
		J. DeGarmo    &  16 &   4362 & 4.86 \\
		D. Renzetti   &  18 &   7877 & 4.47 \\
		R. McKanna    &  47 &  14855 & 4.23 \\
		M. Puls       &  26 &   8379 & 4.18 \\
		King of Light &  24 &   8817 & 4.13 \\
		D. Bernardone & 217 &  76290 & 4.10 \\
		D. D'Amato    & 107 &  36265 & 3.92 \\
		bblum         &  32 &  32382 & 3.76 \\
		\multicolumn{4}{c}{\normalsize\dots} \\
		B. Vergara    &  13 &  15454 & 0.091 \\
		Aoreo         &  21 &  27990 & 0.089 \\
		Zaia          & 368 & 448460 & 0.080 \\
		t0ni          &  85 & 128964 & 0.058 \\
		Burn          &  27 &  60052 & 0.057 \\
		Dirk          &  12 &  21996 & 0.055 \\
		Happy Feet    &  30 &  57888 & 0.040 \\
		@@            &  63 & 199530 & 0.026 \\
		Arvin         &  79 & 108612 & 0.023 \\
		Drazu         & 153 & 221460 & 0.021 \\
		teejusb       &  11 &  11298 & 0.018 \\
		Fraxtil       &  19 &  25612 & 0 \\
	\end{tabular}
	\end{center}
	\caption{Chart authors with the highest/lowest XO\%.}
\end{table}
\begin{table}[t]
	\begin{center}
		\small
	\begin{tabular}{l|r|r|l}
		\bf Author & \bf Charts & \bf Total Steps & \bf FS\% \\
		\hline
		Konami        & 530 & 114623 & 2.29 \\
		bblum         &  32 &  32382 & 1.29 \\
		M. Puls       &  26 &   8379 & 1.16 \\
		R. McKanna    &  47 &  14855 & 1.11 \\
		mudkyp        &  63 &  42792 & 1.09 \\
		S. Venkat     &  24 &  11084 & 0.96 \\
		K. Ward       & 281 &  86475 & 0.89 \\
		xRGTMx        &  19 &  11734 & 0.88 \\
		sssmsm        &  41 &  17219 & 0.85 \\
		D. Bernardone & 217 &  76290 & 0.83 \\
		ATB           &  31 &  20673 & 0.82 \\
		Happy Feet    &  30 &  57888 & 0.82 \\
		\multicolumn{4}{c}{\normalsize\dots} \\
		Hsarus        &  18 &  70162 & 0.070 \\
		Drazu         & 153 & 221460 & 0.057 \\
		@@            &  63 & 199530 & 0.037 \\
		Revolver      &  11 &   8302 & 0.036 \\
		T. Swag       &  13 &  22909 & 0.031 \\
		Dirk          &  12 &  21996 & 0.023 \\
		B. Vergara    &  13 &  15454 & 0.019 \\
		warpdr!ve     &  16 &  19090 & 0.016 \\
		Burn          &  27 &  60052 & 0.015 \\
		teejusb       &  11 &  11298 & 0.009 \\
		t0ni          &  85 & 128964 & 0.002 \\
		S. Tofu       &  26 &  34609 & 0
	\end{tabular}
	\end{center}
	\caption{Chart authors with the highest/lowest FS\%.}
\end{table}
\begin{table}[t]
	\begin{center}
		\small
	\begin{tabular}{l|r|r|l}
		\bf Author & \bf Charts & \bf Total Steps & \bf JK\% \\
		\hline
		King of Light &  24 &   8817 & 12.94 \\
		R. McKanna    &  47 &  14855 & 9.95 \\
		Konami        & 530 & 114623 & 9.63 \\
		P. Shanklin   &  21 &   9834 & 8.91 \\
		M. Puls       &  26 &   8379 & 8.90 \\
		K. Ward       & 281 &  86475 & 8.80 \\
		ATB           &  31 &  20673 & 8.46 \\
		J. DeGarmo    &  16 &   4362 & 8.30 \\
		D. Bernardone & 217 &  76290 & 7.98 \\
		Renard        &  45 &  15035 & 7.94 \\
		C. Foy        & 133 &  52418 & 7.72 \\
		Yoko          &  10 &   4128 & 7.63 \\
		\multicolumn{4}{c}{\normalsize\dots} \\
		bblum         &  32 &  32382 & 1.56 \\
		B. Vergara    &  13 &  15454 & 1.31 \\
		Arvin         &  79 & 108612 & 1.30 \\
		Drazu         & 153 & 221460 & 1.06 \\
		Zaia          & 368 & 448460 & 0.86 \\
		Aoreo         &  21 &  27990 & 0.78 \\
		T. Swag       &  13 &  22909 & 0.70 \\
		@@            &  63 & 199530 & 0.61 \\
		warpdrive     &  16 &  19090 & 0.49 \\
		Dirk          &  12 &  21996 & 0.35 \\
		Burn          &  27 &  60052 & 0.28 \\
		Hsarus        &  18 &  70162 & 0.27 \\
	\end{tabular}
	\end{center}
	\caption{Chart authors with the highest/lowest JK\%.}
\end{table}

% packs
\begin{table}[t]
	\begin{tabular}{l|r|r|l}
		\bf Pack & \bf Charts & \bf Total Steps & \bf XO\% \\
		DDR 1st Mix to Extreme   &  530 & 114623 & 8.03 \\
		r2112                    &   47 &  18377 & 4.50 \\
		the best of r21freak     &  100 &  45156 & 4.22 \\
		the best of r21freak ii  &   48 &  25024 & 4.16 \\
		In The Groove 2          &  222 &  66113 & 4.05 \\
		In The Groove Rebirth+   &  108 &  43758 & 3.99 \\
		r21twins                 &   52 &  22347 & 3.89 \\
		In The Groove 3          &  320 & 106363 & 3.61 \\
		CuoReNeRo MeGaPacK       &  423 & 248625 & 3.45 \\
		In The Groove            & 1408 & 491819 & 3.27 \\
		r21freak Friendship Pack &   47 &  20363 & 3.13 \\
		BemaniBeats 4            &   31 &  18464 & 3.02 \\
		\multicolumn{4}{c}{\normalsize\dots} \\
		Tachyon Epsilon          &  150 & 208830 & 0.064 \\
		SPEEEDCOOOORE 4          &  101 & 123814 & 0.064 \\
		TranceMania              &   80 & 121415 & 0.062 \\
		Cirque du Lykan          &  129 & 160312 & 0.059 \\
		Cirque du Zonda          &   45 &  74890 & 0.057 \\
		Jimmy Jawns              &  109 & 170894 & 0.044 \\
		Getty                    &   26 &  53528 & 0.043 \\
		Tachyon Delta            &   32 &  36712 & 0.038 \\
		Tachyon Gamma            &   32 &  36134 & 0.033 \\
		Oh Henry! Mad Stamina    &   46 & 152326 & 0.028 \\
		Causality Violation      &   10 &  19507 & 0.021 \\
		Fast Track to Brutetown  &   29 &  46082 & 0.020 \\
	\caption{Packs with the highest/lowest XO\%.}
\end{table}
\begin{table}[t]
	\begin{tabular}{l|r|r|l}
		\bf Pack & \bf Charts & \bf Total Steps & \bf FS\% \\
		Subluminal               &   17 &  13418 & 4.70 \\
		Aoreo's Ariginals 2      &   16 &  15222 & 2.42 \\
		DDR 1st Mix to Extreme   &  530 & 114623 & 2.29 \\
		Aoreo's Ariginals        &   31 &  26418 & 2.26 \\
		rocky mount xi           &  113 &  79986 & 0.97 \\
		In The Groove 2          &  222 &  66113 & 0.93 \\
		FA and Chill             &   35 &  22045 & 0.86 \\
		Getty                    &   26 &  53528 & 0.85 \\
		Undertale                &   19 &  14722 & 0.84 \\
		r2112                    &   47 &  18377 & 0.82 \\
		Fort Rapids VI           &   75 &  75563 & 0.77 \\
		Mute Sims 8              &   72 &  47140 & 0.71 \\
		\multicolumn{4}{c}{\normalsize\dots} \\
		SPEEEDCOOOORE 4          &  101 & 123814 & 0.093 \\
		Stamina Showcase         &   38 & 126146 & 0.088 \\
		VocaJawnz II             &  128 & 183153 & 0.084 \\
		Cirque du Zeppelin       &  109 & 102991 & 0.082 \\
		SPEEEDCOOOORE 3          &   66 &  69236 & 0.071 \\
		Causality Violation      &   10 &  19507 & 0.051 \\
		TranceNation             &   41 & 123940 & 0.047 \\
		Oh Henry! Mad Stamina    &   46 & 152326 & 0.046 \\
		Tachyon Epsilon          &  150 & 208830 & 0.040 \\
		Noisiastreamz            &   20 &  41917 & 0.019 \\
		TranceMania 2            &   40 &  64109 & 0.003 \\
		TranceMania              &   80 & 121415 & 0.001 \\
	\caption{Packs with the highest/lowest FS\%.}
\end{table}
\begin{table}[t]
	\begin{tabular}{l|r|r|l}
		\bf Pack & \bf Charts & \bf Total Steps & \bf JK\% \\
		DDR 1st Mix to Extreme   &  530 & 114623 & 9.63 \\
		r2112                    &   47 &  18377 & 8.80 \\
		In The Groove 2          &  222 &  66113 & 8.64 \\
		Gensokyo Holiday         &   87 &  51652 & 7.87 \\
		r21Freak's Friendship Pack 2 &   32 &  15649 & 7.71 \\
		Omnifarious              &   10 &   5594 & 7.53 \\
		r21twins                 &   52 &  22347 & 7.18 \\
		Piece of Cake 7          &   20 &  11554 & 6.97 \\
		In The Groove            & 1408 & 491819 & 6.97 \\
		In The Groove Rebirth+   &  108 &  43758 & 6.97 \\
		TLOES Chapter 1          &   85 &  42201 & 6.89 \\
		ITG Rebirth 2 Beta       &  262 &  99078 & 6.79 \\
		\multicolumn{4}{c}{\normalsize\dots} \\
		TranceMania 2            &   40 &  64109 & 1.03 \\
		Causality Violation      &   10 &  19507 & 0.98 \\
		VocaJawnz II             &  128 & 183153 & 0.98 \\
		Tachyon Epsilon          &  150 & 208830 & 0.94 \\
		Tachyon Delta            &   32 &  36712 & 0.87 \\
		Cirque du Lykan          &  129 & 160312 & 0.87 \\
		Cirque du Veyron         &   31 &  51545 & 0.79 \\
		Cirque du Zeppelin       &  109 & 102991 & 0.77 \\
		Oh Henry! Mad Stamina    &   46 & 152326 & 0.67 \\
		Stamina Showcase         &   38 & 126146 & 0.56 \\
		Cirque du Zonda          &   45 &  74890 & 0.47 \\
		TranceNation             &   41 & 123940 & 0.25 \\
	\caption{Packs with the highest/lowest JK\%.}
\end{table}
